---
title: "Exploration of harvest-rate based fisheries management for data-limited stocks"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This repository ([GA_MSE_HR](https://github.com/shfischer/GA_MSE_HR)) is a mirror of [GA_MSE](https://github.com/shfischer/GA_MSE) and ([GA_MSE_PA](https://github.com/shfischer/GA_MSE_PA)) with the `harvest_rate` branch displayed as default branch.

## Introduction

This repository contains the code for testing a harvest rate-based management procedure and optimising it with a genetic algorithm. The simulation is based on the Fisheries Library in R ([FLR](http://www.flr-project.org/)) and the Assessment for All (a4a) standard MSE framework ([`FLR/mse`](github.com/FLR/mse)) developed during the Workshop on development of MSE algorithms with R/FLR/a4a ([Jardim et al., 2017](https://ec.europa.eu/jrc/en/publication/assessment-all-initiativea4a-workshop-development-mse-algorithms-rflra4a)).

This is the **`harvest_rate`** branch which explores the use of harvest rates. The code is based on code from other branches.

The `master` branch contains the code for the publication: 

> Fischer, S. H., De Oliveira, J. A. A., Mumford, J. D., and Kell, L. T. (2021). Using a genetic algorithm to optimise a data-limited catch rule. ICES Journal of Marine Science. 78: 1311-1323. https://doi.org/10.1093/icesjms/fsab018.

The `PA branch` includes the optimisation with specific risk limits for the ICES precautionary approach (PA) and contains the code for the publication:

> Fischer, S. H., De Oliveira, J. A. A., Mumford, J. D., and Kell, L. T. (2021). Application of explicit precautionary principles in data-limited fisheries management. ICES Journal of Marine Science. 78: 2931-2942. https://doi.org/10.1093/icesjms/fsab169.

The operating models provided as an input are those from the repository [shfischer/wklifeVII](https://github.com/shfischer/wklifeVII) as described in:

> Fischer, S. H., De Oliveira, J. A. A., and Laurence T. Kell (2020). Linking the performance of a data-limited empirical catch rule to life-history traits. ICES Journal of Marine Science, 77: 1914-1926. https://doi.org/10.1093/icesjms/fsaa054.


## Repository structure

> The root folder contains the following R scripts:
> 
> * `OM_hr.R`: This script creates the operating models (OMs),
> * `funs.R` contains functions and methods used for the creation of the operating models and for running the MSE,
> * `funs_GA.R` contains the function used in the optimisation procedure,
> * `run_ms_hr.R` is an R script for running MSE projections and is called from a job submission script
> * `run*.pbs` are job submission scripts which are used on a high performance computing cluster and call `run_ms.R`
> * `analysis_hr.R` is for analysing the results
> 
> The following input files are provided:
> 
> * `input/stocks.csv` contains the stock definitions and life-history parameters
> * `input/brps.rds` contains the FLBRP objects which are the basis for the OMs
> * `input/catch_rates.rds` examples catch rates
> 
> The following outputs summarising the results from running the optimisation are provided:
> 
> * `output/hr_pol_comps_stats.csv` results for exploration of parameters of harvest rate rule for pollack
> * `output/hr_pol_sensitivity.csv` summarised results from sensitivity runs for pollack 
> * `output/hr_all_GA_stats.csv` results for all stocks
> * `output/hr_all_mult_runs_stats.csv` results for all stocks with multiplier and conditional uncertainty caps


## R, R packages and version info

The MSE simulations were run on a high performance computing cluster:
```{r, eval = FALSE}
> sessionInfo()
R version 3.6.1 (2019-07-05)
Platform: x86_64-conda_cos6-linux-gnu (64-bit)
Running under: CentOS Linux 7 (Core)
```

The package versions and their dependencies are recorded with the R package [renv](https://rstudio.github.io/renv/) and stored in the file [renv.lock](https://github.com/shfischer/GA_MSE_HR/blob/master/renv.lock). The exact package version can be restored by cloning this repository, navigating into this folder in R (or setting up a project), installing the renv package

```{r, eval = FALSE}
install.packages("renv")
```

and calling

```{r, eval = FALSE}
renv::restore()
```

See [renv](https://rstudio.github.io/renv/) and the package documentation for details.

The framework is based on the Fisheries Library in R (FLR) framework and uses the [FLR packages](https://flr-project.org/) `FLCore`, `FLash`, `FLBRP`, `ggplotFL`, `mse`. See [renv.lock](https://github.com/shfischer/GA_MSE_HR/blob/master/renv.lock) for version details and sources.

The FLR package versions can also be installed manually with `remotes` (requires suitable tools to compile R packages):
```{r, eval = FALSE}
remotes::install_github(repo = "flr/FLCore", ref = "3d694903b9e6717b86c3e8486fc14ebf92908786")
remotes::install_github(repo = "shfischer/FLash", ref = "d1fb86fa081aaa5b6980d74b07d9adb44ad19a7f", INSTALL_opts = "--no-multiarch") # silenced version of FLash
# INSTALL_opts = "--no-multiarch" to avoid issues in Windows
remotes::install_github(repo = "flr/FLBRP", ref = "3a4d6390abc56870575fbaba3637091036468217", INSTALL_opts = "--no-multiarch")
remotes::install_github(repo = "shfischer/mse", ref = "mseDL2.0", INSTALL_opts = "--no-multiarch")
# and the GA package for running the genetic algorithm
remotes::install_github(repo = "shfischer/GA")
```

For using MPI parallelisation, an MPI backend such as OpenMPI and the R packages `Rmpi` and `doMPI` are required.
